systemfit: A Package for Estimating\\ Systems of Simultaneous Equations in \proglang{R}

### 2007-06-05 paper/trunk/JSS/response_A.tex

\bigskip

{\Large\textbf{Responses to Reviewer A}}
\end{center}

We thank this reviewer for a very helpful set of comments and suggestions
for improving the paper.
The reviewer has made one overall comment, 9 major comments and
several minor comments.
We have structured our reply accordingly.

\section{Overall Comment}
% ########################################################
% ## Review for                                         ##
% ##   systemfit: A Package to Estimate Simultaneous    ##
% ##   Equation Systems in R                            ##
% ##   Arne Henningsen, Jeff D. Hamann                  ##
% ## submitted for publication in                       ##
% ##   Journal of Statistical Software                  ##
% ########################################################
% 
% The paper describes the CRAN package "systemfit" for fitting simultaneous
% equation models in R. Estimation procedures include standard techniques in
% econometrics such as SUR, 2SLS and 3SLS.
% The paper can be divided roughly into three parts: Sections 1/2 explain
% the underlying theory (~12 pages), Sections 3/4 describe the code in systemfit
% and how to use it (~10 pages) and Section 5 reproduces results from various
% textbooks (~8 pages).
% The paper and software are both interesting and mostly well-written: they
% deserve publication in JSS. However, some major and minor comments have to
% be addressed before it can be accepted. In particular, the revision has to
% streamline exposition and notation of standard results, and to combine the
% (established) theory with the implementation more closely (otherwise the reader
% has to wait more than 10 pages before s/he learns something about the package).
% I suggest to eliminate Section 2 in its current form and to re-write the
% description of the theory in a more general and unified way while weaving
% it with the translation into computational tools. As for the software itself,
% several modifications are necessary to make it more intuitive for R users
% and to improve how the underlying concepts are turned into computational 
% tools. More details are described below.
% 
% 
\section{Major Points}
% MAJOR POINTS:
\subsection{Title}
%   o title
% 
%     The title sounds a bit awkward in English: first, "a package *for*
%     estimat*ing*" would be more appropriate, secondly "systems of
%     equations" seems to be preferred over "equation systems" in English.
%
We have changed the title according to these suggestions.

\subsection{Abstract/Introduction}
%   o abstract/introduction
% 
%     Both, abstract and introduction, talk rather generally about
%     systems of equations reviewing rather well-known theoretical
%     results. I would suggest to revise both, focusing on what
%     *can* be done *in R* rather than giving a tutorial what *should*
%     be done *in general*. Of course, it is ok to review some theory,
%     however, practitioners should know what they are doing and the
%     paper should mainly teach them how to do it in R.
%
Both, abstract and introduction, now focus much more
on the capabilities of the \pkg{systemfit} package
rather than on the general theory of estimating systems of equations.

@@

% 
%     The internals of a fitted "systemfit" object could be re-organized. Currently,
%     there are a lot of single letter elements - more standard naming as in "lm"
%     objects etc. would be more desirable.
We have renamed single letter elements (not finished yet).

%     Also, computing the partial t tests

@@

%     arbitrary. Similar comments hold for other arguments, see also below for some
%     more comments. As noted above, the standard in R seems to supply the formula(s)
%     as the first argument and to have then some `method' argument.
We have reversed order of the arguments method and eqns/formula
in systemfit() and systemfitClassic().

@@

% 
%
\section{Minor Points and Typos}
We have corrected the paper according to all of these comments
except for °p.3, l.45° and the second part of °p.3, l.52°.

% MINOR POINTS & TYPOS
% 
%   o p.1, l.3. Is a "theoretical model that is econometrically estimated"
%     a well-defined term?
% 
%   o p.2, Eq.2. The \cdot between the regressor matrix and its coefficients
%     should be omitted (since this is not a scalar multiplication).
% 
%   o p.2, l.42. For symmetry between the two index types, it might be
%     more convenient to denote the equation by i/j and the observation
%     by s/t rather than t/t*, in particular as * is also used later for 
%     other purposes.
% 
%   o p.3, l.45. While it is possible to call u "residual" and \hat u an 
%     "estimated residual", the more standard (and less confusing) terminology
%     is to call u "disturbance" or "error term" and the estimated quantity
%     \hat u "residual".
% 
%   o p.3, l.52. The equation $\sigma^2 = E(u'u)$ is wrong because the 
%     right-hand side is a sum over squared errors. This mistake is repeated
%     throughout the paper. Also (as noted above), no distinction between
%     population and sample covariances is made which leads to confusion.
% 
%   o p.3, l.69. "the GLS is" -> "the GLS estimator is"
%                "called ... SUR" -> "called ... SUR estimator"
% 
%   o p.4, l.72/3. The "E[u|X] = 0" type equations imply (but are not
%     equivalent to) the assumptions of uncorrelated disturbances.
% 
% 
%   o p.4, l.79. The formulation "estimated coefficients are biased" is somewhat
%     sloppy, bias is a property of the estimator.
% 
%   o p.6, l.127 / p.10, l.198. The symbol T is used for different quantities
%     here.
% 
%   o p.12, eq.63. One Sigma is lacking a hat. Now M is used for the number
%     of equations, before it was G.
% 
%   o p.13, l.285. Rather than calling the methods by their full name, it
%     is preferred to refer to the predict or coef method for "systemfit"
%     objects.
% 
%   o p. 13, l.289. The remarks about why not the full code is presented
%     sound very clumsy and should be avoided.
% 
%   o p.13, l.299. "interest" -> "interested"
% 
%   o p.13, l.321. "deviding" -> "dividing"
% 
%   o p.14, l.334. values to arguments should also be set in verbatim,
%     e.g., "``OLS''" -> "\code{"OLS"}"
% 
%   o p.14, l.340. "tilde" -> "\verb/~/"
% 
%   o p.14, l.341. Are only "+" signs allowed or the full standard
%     formula language in R?
% 
%   o p.14, eq.68/69/71. "*" -> "\cdot" (and not in verbatim)
% 
%   o p.14, l.346. "dependant" -> "dependent"
% 
%   o p.17, l.387. The creation of tx should be simplified, e.g., the
%     first six lines could be replaced by
%       tx <- cbind(rbind(diag(5), 0, 0), 0)
% 
%   o p.17, l.405. "large" -> "larger", also say that maxiter = 1 is the
%     default.
% 
%   o p.18, Tab.1. I find it a bit confusing that the argument ist called 
%     "rcovformula" but does not expect a formula (in the R sense). Also,
%     type 0 should have an alternative string specification. A similar
%     argument holds for "formula3sls".
%

### 2007-06-05 paper/trunk/systemfit_abstract.tex
The abstract and the introduction now focus much more on the capabilities of systemfit rather than on the general theory of estimating systems of equations; added note about this in the response to reviewer A
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@709 591db2bd-e0a0-4d22-8c19-2192dbb7da31

\Abstract{
Many statistical analyses (econometrics, biostatistics and
experimental design) are based on models containing systems of
structurally related equations.
In cases where cross-equation disturbances are correlated,
full information methods are required \citep{zellner62}.
If exogenous variables are stochastically dependent
on the disturbances in the system,
then instrumental variable estimation methods should be used
\citep{zellner62b}
The package \pkg{systemfit} provides the capability
to estimate systems of linear equations
within the \proglang{R} programming environment.
}

>>>>

\Abstract{
Many statistical analyses (e.g.\ in econometrics, biostatistics and
experimental design) are based on models containing systems of
structurally related equations.
The \pkg{systemfit} package provides the capability
to estimate systems of linear equations
within the \proglang{R} programming environment.
For instance, this package can be used for estimations
by ``Ordinary Least Squares'' (OLS),
``Seemingly Unrelated Regression'' (SUR),
and the instrumental variable (IV) methods
``Two-Stage Least Squares'' (2SLS) and
``Three-Stage Least Squares'' (3SLS),
where SUR and 3SLS estimations can optionally be iterated.
Furthermore, the \pkg{systemfit} package provides tools
for several statistical tests.
It has been tested on a variety of datasets
and the reliability of its results has been shown.
}

### 2007-06-05 paper/trunk/systemfit_intro.tex
The abstract and the introduction now focus much more on the capabilities of systemfit rather than on the general theory of estimating systems of equations; added note about this in the response to reviewer A
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@709 591db2bd-e0a0-4d22-8c19-2192dbb7da31

Many theoretical models consist of more than one equation.
If these models are econometrically estimated,
the disturbance terms of these equations are likely
to be contemporaneously correlated,
because unconsidered factors
that influence the disturbance term in one equation
probably influence the disturbance terms in other equations.
Ignoring this contemporaneous correlation
and estimating these equations separately
leads to inefficient parameter estimates.
However, estimating all equations simultaneously,
taking the covariance structure of the residuals into account,
leads to efficient estimates.
This estimation procedure is generally called
°Seemingly Unrelated Regression° (SUR) \citep{zellner62}.
Another reason to estimate a system of equations simultaneously are
cross-equation parameter restrictions.%
\footnote{
Especially the economic theory suggests many cross-equation parameter
restrictions (e.g.\ the symmetry restriction in demand models).
}
These restrictions can be tested and/or imposed only in a simultaneous
estimation approach.

@@

The \pkg{systemfit} package provides the capability to estimate
systems of linear equations in \proglang{R}
\citep{r-project}.
Although systems of linear equations can be estimated
with several other statistical and econometric software packages
(e.g.\ \proglang{SAS}, \proglang{EViews}, \proglang{TSP}),
\pkg{systemfit} has several advantages.
First, all estimation procedures are publicly available in the source code.
Second, the estimation algorithms can be easily modified to meet specific
requirements.
Third, the (advanced) user can control estimation details generally
not available in other software packages by overriding reasonable defaults.

>>>>

Many theoretical models consist of more than one equation.
If these models are econometrically estimated,
the disturbance terms of these equations are likely
to be contemporaneously correlated,
because unconsidered factors
that influence the disturbance term in one equation
probably influence the disturbance terms in other equations.
Ignoring this contemporaneous correlation
and estimating these equations separately
leads to inefficient parameter estimates.
However, estimating all equations simultaneously
with a °Generalized Least Squares° (GLS) estimator,
which takes the covariance structure of the residuals into account,
leads to efficient estimates.
This estimation procedure is generally called
°Seemingly Unrelated Regression° (SUR) \citep{zellner62}.
Another reason to estimate a system of equations simultaneously are
cross-equation parameter restrictions.%
\footnote{
Especially the economic theory suggests many cross-equation parameter
restrictions (e.g.\ the symmetry restriction in demand models).
}
These restrictions can be tested and/or imposed only in a simultaneous
estimation approach.

@@

The \pkg{systemfit} package provides the capability to estimate
systems of linear equations in \proglang{R}
\citep{r-project}.
Currently, the estimation methods
°Ordinary Least Squares° (OLS),
°Weighted Least Squares° (WLS),
°Seemingly Unrelated Regression° (SUR),
°Two-Stage Least Squares° (2SLS),
°Weighted Two-Stage Least Squares° (W2SLS), and
°Three-Stage Least Squares° (3SLS)
are implemented.%
\footnote{
In this context,
the term °weighted° in °Weighted Least Squares° (WLS) and
°Weighted Two-Stage Least Squares° (W2SLS) means
that the \emph{equations} might have different weights
and \emph{not}
that the \emph{observations} have different weights.
}
The WLS, SUR, W2SLS, and 3SLS estimates can be based
either on one-step (OLS or 2SLS) (co)variances
or these estimations can be iterated,
where the (co)variances are calculated from the estimates of the previous step.
Furthermore,
the \pkg{systemfit} package
provides statistical tests for parameter restrictions
and for testing the consistency of the 3SLS estimation.

Although systems of linear equations can be estimated
with several other statistical and econometric software packages
(e.g.\ \proglang{SAS}, \proglang{EViews}, \proglang{TSP}),
\pkg{systemfit} has several advantages.
First, all estimation procedures are publicly available in the source code.
Second, the estimation algorithms can be easily modified to meet specific
requirements.
Third, the (advanced) user can control estimation details generally
not available in other software packages by overriding reasonable defaults.
